---
output:
  pdf_document: default
  html_document: default
---



This data comes from Kaggle and stored in local drive.

There are a few articles I found on the web helping solving the issues with Ames Housing :

* https://topepo.github.io/caret/recursive-feature-elimination.html
* http://www.rpubs.com/skorpio11/housing







```{r}
setwd("/Users/Ronny/EDX_MachineLearning/Housing")
train <- read.csv("train.csv")
test <- read.csv("test.csv")
```



Only picks up numeric columns and see correlation between them
```{r}
nums <- unlist(lapply(train, is.numeric))  
train <- train[,nums]

```


Another method to do this is via dplyr
```{r}
library(dplyr)
select_if(train, is.numeric)
```


If you look at summary below, you notice there are some NAs

```{r}
summary(train)
```

Replace all NAs with average

```{r}
train$LotFrontage[is.na(train$LotFrontage)] = mean(train$LotFrontage, na.rm = TRUE)
train$GarageYrBlt[is.na(train$GarageYrBlt)] = train$YearBuilt
train$MasVnrArea[is.na(train$MasVnrArea)] = mean(train$MasVnrArea,na.rm = TRUE)
```

** Not running this code but it is good to know this function **
Dealing with remaining NAs, prob about 8 rows left in MasVnArea. Just remove those 8 rows

```{r}

row.has.na <- apply(train,1,function(x){any(is.na(x))})
sum(row.has.na)
train <- train[!row.has.na,]

```

Now let's check summary to confirm NA has been removed.

```{r}
summary(train)
```


# Using Corrplot to see correlation between features

From the plot below you can see the following observations between features and SalePrice

```{r}
library(corrplot)
corr <- cor(train)
corrplot(corr, method="circle", tl.cex=0.6)   #tl.cex to adjust the label size
```


I'm going to reduce the number of features by using findcorrelation function to show features that are highly correlated > 0.6
You can see the plot gives less features and you can see correlation between them.

```{r}
library(caret)
highcorr <- findCorrelation(corr,cutoff = 0.6,names=TRUE)
train <- train[,highcorr]

corr <- cor(train)
corrplot(corr, method="circle", tl.cex=0.6)   #tl.cex to adjust the label size

```

Observations based on the reduced plot :
1. We can see all the important features in column 1
2. GrLivArea highly correlated with TotRmsAbvGrd and X2ndFlrSf
3. YearBuilt and GarageYrBlt also highly correlated

Since some of these features are highly correlated, we can remove them

```{r}
library(dplyr)
train <- train[,-c(6,7,10)]
corr <- cor(train)
corrplot(corr, method="circle", tl.cex=0.6)   #tl.cex to adjust the label size
str(train)
```


I'm now left with 5 features for non numeric.
1.SalePrice   
2.GrLivArea   
3.OverallQual
4.X1stFlrSF   
5.GarageCars




# Recursive Feature Elimination (not happy with the outcome.... reviw later)

For a specific model, a set of functions must be specified in rfeControl$functions. Sections below has descriptions of these sub-functions. There are a number of pre-defined sets of functions for several models, including: linear regression (in the object lmFuncs), random forests (rfFuncs), naive Bayes (nbFuncs), bagged trees (treebagFuncs) and functions that can be used with caret’s train function (caretFuncs). The latter is useful if the model has tuning parameters that must be determined at each iteration.

```{r}
x <- select(train,-SalePrice)
y <- train[,38]

subsets <- c(1:5, 10, 15, 20, 25)
ctrl <- rfeControl(functions = rfFuncs,
                   method = "repeatedcv",
                   repeats = 5,
                   verbose = FALSE)

lmProfile <- rfe(x, y,
                 rfeControl = ctrl)
lmProfile
```

I'm going to use LM to figure out var important for my features


```{r}
library(caret)
control <- trainControl(method="repeatedcv", number=10, repeats=3)

# train the model
model <- train(SalePrice~., data=train, method="lm", preProcess="scale", trControl=control)

# estimate variable importance
importance <- varImp(model, scale=FALSE)

# summarize importance
print(importance)

# plot importance
plot(importance)

```


From the above plot, I'm gonna pick up features up to X2ndFlrSF and combine these with other non numeric features. 
Will use random forest to perform this modelling later

Now let's do some visualisation to check non numeric features and how they link to sale price.

```{r}
library(ggplot2)
setwd("/Users/Ronny/EDX_MachineLearning/Housing")
train2 <- read.csv("train.csv")
x <- select_if(train2,is.factor)
x$SalePrice <- train2$SalePrice



# remove some of these columns as they do not have variability 

x <- select(x,-c('Street','Alley','Utilities','Condition2','RoofMatl','Heating','CentralAir','PavedDrive','PoolQC','Fence','MiscFeature'))

summary(x)
```

Based on the summary above, you can see some of the columns only contains 2 factors and probably
not very usefull at all. They can be removed. 

Removed NA for non numeric
```{r}
x$MasVnrType[is.na(x$MasVnrType)] <- 'None'
x$BsmtCond[is.na(x$BsmtCond)] <- 'TA'
x$BsmtExposure[is.na(x$BsmtExposure)] <- 'No'
x$BsmtFinType2[is.na(x$BsmtFinType2)] <- 'Unf'
x$BsmtFinType1[is.na(x$BsmtFinType1)] <-'Unf'
x$BsmtQual[is.na(x$BsmtQual)] <- 'TA'
x$Electrical[is.na(x$Electrical)] <- 'SBrkr'
x$GarageType[is.na(x$GarageType)] <- 'Attchd'
x$GarageQual[is.na(x$GarageQual)] <- 'TA'
x$GarageCond[is.na(x$GarageCond)] <- 'TA'
x$FireplaceQu[is.na(x$FireplaceQu)] <- 'TA'
x$GarageFinish[is.na(x$GarageFinish)] <- 'Unf'
x <- select_if(x,is.factor)
summary(x)
```

Now, I'm gonna combine train which is numeric to x which is non numeric back to 1 data frame
```{r}
train <- cbind(train,x)
str(train)
```


Okay, let's do random forest to see the prediction if it is better than lm where MAE around $30k.
```{r}

rf <- train(SalePrice~.,method='rf',data=train)
rf$results
```

From the results above, you can see the best result is with mtry 92
Now, create file for submission

```{r}
myf <- names(select(train,-SalePrice))
test <- test[,c('Id',myf)]


#remove NA
test$GarageYrBlt[is.na(test$GarageYrBlt)] <- 1978
test$GarageCars[is.na(test$GarageCars)] <- 1.766
test$MSZoning[is.na(test$MSZoning)] <- 'RL'
test$BsmtFinSF1[is.na(test$BsmtFinSF1)] <- 439.2
test$GarageType[is.na(test$GarageType)] <- 'Attchd'
test$BsmtFinType1[is.na(test$BsmtFinType1)] <- 'Unf'
test$BsmtFinType2[is.na(test$BsmtFinType2)] <- 'Unf'
test$GarageCond[is.na(test$GarageCond)] <- 'TA'
test$GarageQual[is.na(test$GarageQual)] <- 'TA'
test$BsmtExposure[is.na(test$BsmtExposure)] <- 'No'
test$BsmtCond[is.na(test$BsmtCond)] <- 'TA'
test$BsmtQual[is.na(test$BsmtQual)] <- 'TA'
test$FireplaceQu[is.na(test$FireplaceQu)] <- 'TA'
test$GarageFinish[is.na(test$GarageFinish)] <- 'Unf'
test$Exterior1st[is.na(test$Exterior1st)] <- 'VinylSd'
test$Exterior2nd[is.na(test$Exterior2nd)] <- 'VinylSd'
test$MasVnrType[is.na(test$MasVnrType)] <- 'BrkFace'
test$SaleType[is.na(test$SaleType)] <- 'WD'
test$Functional[is.na(test$Functional)] <- 'Typ'
test$KitchenQual[is.na(test$KitchenQual)] <- 'TA'



```



Now apply random forest to test data and create submission file
```{r}

SP <- predict(rf,test)
test$SalePrice <- SP

submit <- data.frame(Id = test$Id, SalePrice = test$SalePrice)
write.csv(submit, file = "housing2.csv", row.names = FALSE)

```




Play around with box plot to go through non numeric features manually at the moment.

```{r}
library(ggplot2)
train2 %>% ggplot(aes(y=SalePrice/100000,x=Condition2)) + geom_boxplot()

```

These are Non Numeric Features
MSZoning
LandContour
Condition1
Condition2
Neighborhood
HouseStyle
ExterQual
Foundation
HeatingQC
CentralAir
KitchenQual
FireplaceQu
GarageType
SaleType
SaleCondition

These are numeric features
OverallQual			
GrLivArea			
GarageCars	
YearBuilt			
TotalBsmtSF


Now, I'm gonna use the above features against the initial dataset.

```{r}
myfeatures <- c(
'MSZoning',
'LandContour',
'Condition1',
'Condition2',
'Neighborhood',
'HouseStyle',
'ExterQual',
'Foundation',
'HeatingQC',
'CentralAir',
'KitchenQual',
'SaleType',
'OverallQual',			
'GrLivArea',		
'GarageCars',	
'YearBuilt'	,		
'TotalBsmtSF',
'SaleCondition',
'SalePrice')

train <- read.csv("train.csv")
train <- train[,myfeatures]

summary(train)


```

# test using decision tree

```{r}
library(rpart)
dt <- rpart(SalePrice~.,data=train)

plot(dt, margin=0.1)
text(dt, cex=0.7)
dtpredic
```


```{r}
library(caret)
control <- trainControl(method="repeatedcv", number=10, repeats=3)

# train the model
model <- train(SalePrice~., data=train, method="rf", preProcess="scale", trControl=control)

# estimate variable importance
importance <- varImp(model, scale=FALSE)

# summarize importance
print(importance)

# plot importance
plot(importance)
```


# havent tested the one below

Automatic selection for features you can use below website to see more details
https://machinelearningmastery.com/feature-selection-with-the-caret-r-package/

```{r}
# ensure the results are repeatable
set.seed(7)
# load the library
library(mlbench)
library(caret)
# load the data
data(train)
# define the control using a random forest selection function
control <- rfeControl(functions=rfFuncs, method="cv", number=10)
# run the RFE algorithm
results <- rfe(PimaIndiansDiabetes[,1:8], PimaIndiansDiabetes[,9], sizes=c(1:8), rfeControl=control)
# summarize the results
print(results)
# list the chosen features
predictors(results)
# plot the results
plot(results, type=c("g", "o"))

```

