---
title: "My Playground"
output: html_notebook
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


In this workbook, I will highlight some of the skills that I need  
to prove on and put the codes here. 

# R markdown Cheat Sheets
If you want to end a line, do two spaces before pressing enter.  
A new paragraph will appear below otherwise it will continue

* to do header use #
* ordered list just type 1, 2 etc
* italic  *...*
* bold **...**

# Things I would like to improve with my coding
* ggplot
* dplyr
* sample
* rnorm, qqplot etc
* what charts they use with matrices


# GGPLOT Practise

```{r}

library(dslabs)
data(murders)
head(murders)
```


```{r}
murders %>% ggplot(aes(x=region,y=population, fill=(region))) + geom_boxplot()
```

I think the key with ggplot is as follow :
* built ggplot and aes
* you can add any charts with + sign


```{r}
data(cars)
cars %>% ggplot(aes(x=speed,y=dist)) + geom_dotplot()
```

```{r}
gapminder %>% ggplot(aes(y=infant_mortality,x=region)) + geom_boxplot()
```

to fix the label so you can see them you use the following.
You can also use the sample data below to understand how to use boxplot

```{r}

gapminder %>% ggplot(aes(y=infant_mortality,x=region)) + geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

```


The code is still not right but you can also sort the box plot..
https://rafalab.github.io/dsbook/case-study-trends-in-world-health-and-economics.html#stratify-and-boxplot

Finish off later

```{r}
fac <- factor(c("Asia", "Asia", "West", "West", "West"))
levels(fac)
#> [1] "Asia" "West"

value <- c(10, 11, 12, 6, 4)
fac <- reorder(fac, value, FUN = mean)
levels(fac)
#> [1] "West" "Asia"


p <- gapminder %>% 
  filter(year == past_year & !is.na(gdp)) %>%
  mutate(region = reorder(region, dollars_per_day, FUN = median)) %>%
  ggplot(aes(region, dollars_per_day, fill = continent)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  xlab("")
p

```



```{r}
n_distinct(gapminder$region)

p <- gapminder %>% 
  filter(year == past_year & !is.na(gdp)) %>%
  ggplot(aes(region, dollars_per_day)) 
p + geom_boxplot() 
```


# **Matrices** 

You can see sweep function which basically apply colmeans against 2 (column) which means  
it will deduct the numbers
```{r}
a <- c(2,3,4,1,2,3)  
a <- matrix(a,2,2)  

sweep(a,2,colMeans(a))
```







